---
title: "daily_problems"
output: github_document
date: "2023-12-28"
---
24th January 2024
Given a 2D matrix of characters and a target word, write a function that returns whether the word can be found in the matrix by going left-to-right or up-to-down.

For example, given the following matrix:
[['F','A','C','I'], 
 ['O','B', 'Q', 'P'],
 ['A','N', 'O', 'B'],
 ['M', 'A', 'S', 'S']]
and the target word 'FOAM' you should return true, since it's the leftmost column. Similarily, given the target word 'MASS', you should return true, since it's the last row.

left to right
up to down

target <- "FOAM" #target name
matrix <- matrix(c('F', 'A','C','I', 'O','B', 'Q', 'P', 'A','N', 'O', 'B', 'M', 'A', 'S', 'S'), nrow=4) #create matrix
for (nrow in 1:nrow(matrix)){
  col <- ncol(matrix)
left_right_word <- matrix[nrow,1:col] #check left to right first
maybe_word <- paste(left_right_word, collapse="") #remove quotes and space
print(identical(maybe_word, target)) #see if TRUE or FALSE
left_right_word <- matrix[1:col,nrow] #check up to down
print(identical(maybe_word, target))  #see if TRUE or FALSE}

28th December 2023

Compute the running median of a sequence of numbers. That is, given a stream of numbers, print out the median of the list so far on each new element.

Recall that the median of an even-numbered list is the average of the two middle numbers.

For example, given the sequence [2, 1, 5, 7, 2, 0, 5], your algorithm should print out:

2
1.5
2
3.5
2
2
2

```{r}
seq <- c(5,3,2,4,5,2)
len <- length(seq)
new_list <- list()
for (x in 1:len){
  new_list = append(new_list, seq[x]) 
  i <- unlist(new_list)
  med <-median(i)
  print(med)
}
```
Example given in question:
```{r}
seq <- c(2, 1, 5, 7, 2, 0, 5)
len <- length(seq)
new_list <- list()
for (x in 1:len){
  new_list = append(new_list, seq[x]) 
  i <- unlist(new_list)
  med <-median(i)
  print(med)
}
```

